PEP Access

### 2018-09-20 interactiveMap.Rmd
Initial commit

mada.district@data %>%
  select(!!vars) %>%
  mutate_at(vars(starts_with("year")), funs(replace(., is.na(.), 0))) %>%
  mutate(avg.bites100k = (select(., starts_with("year")) %>% rowSums())/4/(midpops/1e5)) -> dist.data
dist.data %>% 
  filter(district)
## subset out Analamanga (IPM) + Haute Matsiatra (Fianarantsoa)

>>>>

mada.district@data %>%
  select(!!vars) %>%
  mutate_at(vars(starts_with("year")), funs(replace(., is.na(.), 0))) %>%
  mutate(avg.bites100k = (select(., starts_with("year")) %>% rowSums())/4/(midpops/1e5),
         dogs_min = round(midpops/25), dogs_max = round(dist.data$midpops/5)) -> dist.data

## set to NA all non-reporters!
